---
author: Cody Dettlaff
title: Conservationist
format:
  classic-cv-pdf: default
cvfooter:
  left: "I am"
  right: "here"
cvcolor: 58748F #without `#`
cvfont: fetamont #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: MPS Candidate, Cornell University
    right: Ithaca, NY
  - title: College
    left: Agriculture and Life Sciences
    right: Department of Natural Resources and the Environment
  - title: Skills
    left: GIS, Field Ecology, SCUBA, R
    right: cnd34@cornell.edu
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Professional Summary

Environmental consultant in training and U.S. Marine Corps veteran with 9 years of proven leadership in global operations. Specialized in risk analysis, GIS, and ecological assessment, with applied research on sturgeon habitats, reef ecosystems, and marine bioacoustics. Experienced in project management, stakeholder engagement, and data-driven decision support. Adept at bridging field ecology, spatial analysis, and risk management to deliver actionable solutions for conservation, infrastructure, and resource management challenges.

# Research Experience

```{r}
#| label: research experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "GIS Analyst and Research Collaborator", "Huson River Project Cornell Lab of Ornithology", "2023 - 2024",
    "NA", c("Delivered spatial analysis in ArcGIS Pro to map Atlantic Sturgeon habitat use and migration routes in the Hudson River.", "Assessed risks from anthropogenic pressures", "Produced conservation risk maps and predictive models for agency and stakeholder decision making.", "Project outcomes supported state and regional managemnet planning."),
    "Independent Research", "Cornell University", "2023 - 2024", "NA", c("Designed and executed multi site reserach across Hawaii and the Bahamas.", "Applied quantitative ecological methods and risk-based observation strtegies", "Findings highlighted species roles as potential reef health indicators providing insight for resource management", "Secured partial funding through research grants"),
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Professional Experience

```{r}
#| label: professional experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
   
    "CFL-2 Trainer", "Crossfit Vertical", "Sep. 2023 - Present",
    "N/A", c("Manage classes of 150+ athletes, fostering teamwork, resilience, and goal achievement.", "Holds a certification of Adaptive and Inclusive Trainer"),
    "Outreach Peer Counselor", "Cornell University", "Sep. 2022 - Present", "Undergraduate Admissions", c("Lead a team of 4 supporting veteran admissions, recruitment, and data security."),
    "Dive Master", "Cornell University", "Sep. 2023 - May. 2024", "Outdoor Recreation", c("Fill this out later"),
    "Infantry Unit Leader", "United States Marine Corps", "Oct. 2012 - Jul. 2021", "Department of Computer & Information Science", c("Directed high-risk operations with teams of up to 63 personnel across deployments in the Balkans, Pacific, and Middle East.", "Authored multiple Standard Operating Procedures later adopted at the battalion and company level.", "Conducted risk assessments, resource allocation, and logistics management for projects valued at 3.5 million dollars.", "Trained and advised multinational partner forces, strengthening coalition operations and cross-cultural coordination.", "Recognized with Navy and Marine Corps Achievement Medals (2) for leadership and mission success.")
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "MPS in Natural Resources and the Environment", "Cornell University", "Ithaca, New York", "Aug. 2025 - Aug. 2026", c("Capstone: Predictive modling of Mesophotic Reef Systems", "Fill this out later"),
    "B.S. in Biological Sciences", "Cornell University", "Ithaca, New York", "Jun. 2022 - May. 2025", c("Concentration: Marine Biology", "Minor: Environment and Sustainability")
) |>
    cvevents(when = "dates", what = "degree", where = "uni", details = "details")
```
